### 2021-04-09 Chapter-6/Chapter-6.tex
Updates from Overleaf

In conclusion, this dissertation research develops practical techniques for side-channels in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effeteness and generality of our proposed method.  We also open source the tool in the dissertation to facilitate the future research in the area.

@@

>>>>

In conclusion, this dissertation research develops practical techniques for practical and precise side-channel analysis in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effeteness and generality of our proposed method.  We also open source the tool in the dissertation to facilitate future research in the area.

@@

\textbf{Compiler-assisted Side-channel Vulnerability Analysis And Mitigation.}

\textbf{Static Side-channel Quantification.}
